Peer Assessment 1
========================================================

###Step 1: Load data into R

```{r}

data <- read.table(unz("activity.zip", "activity.csv"), header=T, sep=",");
head(data)

```

###Step 2: Preprocessing

I will pull out results with associated numbers of steps (no NA values), and show the head of the leftover data.

```{r}

steps_data <- data[!is.na(data$steps),];
head(steps_data)

```


###Step 3: Make a histogram of the total number of steps in a day.

First, add up the number of steps per day, first by verifying that each day has a full set of measurements.

```{r}
dim(table(factor(steps_data$date)))
max(table(factor(steps_data$interval)))
min(table(factor(steps_data$interval)))

```

Since there are 53 dates included, and each possible interval appears 53 times, I am satisfied. Now I will add up steps per day, and make a histogram.

```{r}
steps <- rep(0, 53)
for (i in 1:53) {
  steps[i] <- sum(steps_data$steps[(1 + 60/5*24*(i-1)):(60/5*24*i)])
  x <- (1 + 60/5*24*(i-1))
  y <- (60/5*24*i)
}

hist(steps)

```

###Step 4: What is the mean and the median number of steps per day?

```{r}
mean(steps)
median(steps)


```


###Step 5: Time series of average steps taken